Tickle me BERT: Using laughter to probe pre-trained encoders for dialogue act recoginiton

### 2019-12-09 reports/ACL2020 Paper/acl2020-paper.tex
new title; add to discussion

\title{Pre-trained encoders for dialogue: The case of laughter}

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
\begin{tabular}{@{}lrrrr@{}}
\toprule
           & \multicolumn{2}{c}{SWDA}                          & \multicolumn{2}{c}{AMI-DA}                        \\ \midrule
           & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} \\
\texttt{BERT-FT}    & 45.99                  & 76.93                    & 50.03                  & 66.95                    \\
\texttt{BERT+ID-FT} & 45.48                  & 77.02                    & 46.56                  & 68.66                    \\
\texttt{BERT+CC-FT} & 47.78                  & 77.35                    & 48.72                  & 66.58                    \\ \midrule
\texttt{BERT-FZ}    & 7.75                   & 55.61                    & 14.44                  & 46.60                    \\
\texttt{BERT+ID-FZ} & 6.46                   & 52.30                    & 14.43                  & 48.07                    \\
\texttt{BERT+CC-FZ} & 5.76                   & 51.14                    & 12.56                  & 42.42                    \\ \bottomrule
\end{tabular}
  \caption{Comparison of macro-average F1 and accuracy  with further in-domain (\texttt{ID}) and cross-domain (\texttt{CC}) dialogue pre-training,
    for both the frozen (\texttt{FZ}) and fine-tuned (\texttt{FT}) conditions.}
  \label{table:exp3}
\end{table}

@@

\begin{itemize}
  \item RoBERTa training scheme finds that next sentence prediction is of little importance. Is this true for us too? (suspect not due to discourse importance). see: https://github.com/huggingface/transformers/issues/1622
  \item Issues related to working with transcribed speech: Different kinds of laughter are all represented by the same token. Does transcription orthography capture prosody? We know prosidy is useful for DAR (Jurafsky).
  \item future work: pre-training on very large un-labeled dialogue corpora. How does text chat transfer to the spoken/transcribed setting?
  \item Laughter is more helpful in SWDA than in AMI-DA. 
  \item The point above can also explain why our models better on SWDA: just a larger proportion of stuff that interlocutors rely on is in the transcription.
\end{itemize}

>>>>

\title{Tickle me BERT: Using laughter to probe pre-trained encoders for dialogue act recoginiton}

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
\begin{tabular}{@{}lrrrr@{}}
\toprule
           & \multicolumn{2}{c}{SWDA}                          & \multicolumn{2}{c}{AMI-DA}                        \\ \midrule
           & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} \\
\texttt{BERT-FT}    & 45.99                  & 76.93                    & 50.03                  & 66.95                    \\
\texttt{BERT+ID-FT} & 45.48                  & 77.02                    & 46.56                  & 68.66                    \\
\texttt{BERT+CC-FT} & 47.78                  & 77.35                    & 48.72                  & 66.58                    \\ \midrule
\texttt{BERT-FZ}    & 7.75                   & 55.61                    & 14.44                  & 46.60                    \\
\texttt{BERT+ID-FZ} & 6.46                   & 52.30                    & 14.43                  & 48.07                    \\
\texttt{BERT+CC-FZ} & 5.76                   & 51.14                    & 12.56                  & 42.42                    \\ \bottomrule
\end{tabular}
  \caption{Comparison of macro-average F1 and accuracy  with further in-domain (\texttt{ID}) and combined corpus (\texttt{CC}) dialogue pre-training,
    for both the frozen (\texttt{FZ}) and fine-tuned (\texttt{FT}) conditions.}
  \label{table:exp3}
\end{table}

@@

Although our experiments with further pre-training were inconclusive, \citet{baoPLATOPretrainedDialogue2019} finds that further pre-training BERT on a large-scale Reddit and Twitter corpus is helpful for response selection.
Further pre-training may be helpful for DAR too, if the in-domain or cross-domain corpus is large enough.

It remains an open question how well the text chat domain transfers to transcribed dialogue and what pre-training schemes are best for the dialogue domain.
The training scheme for RoBERTa \citep{liuRoBERTaRobustlyOptimized2019}, for example, leaves out next sentence prediction as a pre-training task because they do not find that it improves performance on question answering and natural language inference tasks.
The same may not be true of dialogue, however.

%\begin{itemize}
  %\item RoBERTa training scheme finds that next sentence prediction is of little importance. Is this true for us too? (suspect not due to discourse importance). see: https://github.com/huggingface/transformers/issues/1622
  %\item Issues related to working with transcribed speech: Different kinds of laughter are all represented by the same token. Does transcription orthography capture prosody? We know prosidy is useful for DAR (Jurafsky).
  %\item future work: pre-training on very large un-labeled dialogue corpora. How does text chat transfer to the spoken/transcribed setting?
  %\item Laughter is more helpful in SWDA than in AMI-DA. 
  %\item The point above can also explain why our models better on SWDA: just a larger proportion of stuff that interlocutors rely on is in the transcription.
%\end{itemize}
